Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-09 paper.tex

We looked at both $e^x$ as well as TODO WHAT OTHER SCHEME using GET PARAMETERS

@@

>>>>

We looked at both $e^x$ as well as TODO WHAT OTHER SCHEME using WHAT WERE THE PARAMETERS - Coarse and Fine Num Steps

@@

Now with 3 different parallel implementations, two in time wiht the parareal, one in space,  we compare across TODO WESLSEY
